### 2017-04-14 paper/oopsla17-submission/intro2.tex
tweak intro

\section{Introduction}
\label{sec:introduction}

@@

Our \emph{second contribution} (\autoref{sec:learning})
solves this problem with a simple, yet expressive, representation called
a \emph{Bag-of-Abstracted-Terms (BOAT)} wherein
%
(1)~each program is represented by the \emph{bag}
    or multiset of (sub-)~terms that appears inside
    it; and
%
(2)~each (sub-)~term $t$ is \emph{abstracted} as
    a vector $[f_1(t), \ldots, f_n(t)]$, where
    each $f_i$ is a \emph{feature abstraction}
    that maps a term to a numeric value.
%
We can model the blame labels with a simple feature
abstraction (\eg does-change-in-fix).
%
We can even account for \emph{contextual} information like
the features of the parent- and child- terms by
concatenating the feature vectors of each term with those
of its parent and children.
%
We have found this representation to be particularly
convenient as it gives us flexibility
in modeling the syntactic and semantic structure of programs
while retaining compatibility with off-the-shelf classifiers,
in contrast to, \eg, \citet{Raychev2015-jg}, who had to develop
their own variants of classifiers to obtain their results.

>>>>

\section{\textbf{Introduction}}
\label{sec:introduction}

@@

Our \emph{second contribution} (\autoref{sec:learning})
solves this problem with a simple, yet expressive, representation called
a \emph{Bag-of-Abstracted-Terms (BOAT)} wherein
each program is represented by the \emph{bag}
or multiset of (sub-)~terms that appears inside
it; and further, each (sub-)~term is \emph{abstracted}
as a feature vector comprising the numeric values
returned by \emph{feature abstraction} functions
that applied to the term.
%
We can model the blame labels with a simple feature
abstraction (\eg is-changed-in-fix).
%
We can even account for \emph{contextual} information
like the features of the parent- and child- terms by
\emph{concatenating} the feature vectors of each term
with those of its parent and children.
%
We have found this representation to be particularly
convenient as it gives us flexibility in modeling the
syntactic and semantic structure of programs while
retaining compatibility with off-the-shelf classifiers,
in contrast to, \eg, \citet{Raychev2015-jg}, who had
to develop their own variants of classifiers to obtain
their results.
